Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-08-15 letters/reply_referee.tex

  \item \emph{Page 18:
        it is stated that the decay width decreases like R-6 but in page 20 it decreases exponentially.}\\
        The reason is that it discusses different interatomic distances being
        the energy transfer distance $R$ ($R^{-6}$) and the electron
        transfer distance $Q$ ($e^{-Q}$) which can both be found in previous and
        coming papers about ETMD(3) (J. Chem. Phys. \textbf{138}, 014305 (2013).
        and Fasshauer \emph{et al.} Mol. Phys. (2016), submitted.):
\begin{center}
 \includegraphics[width=6cm]{../pics/coord_systems.pdf}
\end{center}
        Both on page 18 and 20, these distances are very clearly characterized
        in terms involved atom types or groups and which process is ongoing.
        To further clarify the matter, the sentences on page 18 now read:\\
        Two aspects have to be taken into account: an energy shift of the peaks
        due to different charge distances {\color{blue}{$d$}} in the
        final state (i.e. the interatomic Xe-Xe
        distance) and the decrease of the decay width with $R^{-6}$,
        $R$ being the distance between the electron transfer unit and the xenon
        atom ionized in the final state.
        The larger the distance between the xenon atoms, the higher are the
        energies of the secondary electrons{\color{blue}{. For the case of xenon
        atoms on argon surfaces this at the same time means a larger distance
        between the Ar-Xe pair involved in the electron transfer and the
        electron emitting xenon atom. Hence, the decay widths are smaller.}}
        Therefore, a
        significant contribution from ETMD(3) compared to ICD is only
        seen if the two xenon atoms reside on two adjacent
        surfaces.

  \item \emph{Page 29:
        the efficiency of ICD is found below unity for clusters having few Xe atoms. I guess this is because in these clusters ICD and ETMD are closed for some Argon atoms which are anyway ionized. Maybe a statistical model may explain it. The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}\vspace{0.3cm}\\
        This is a good point from the referee. We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{We found an Ar 3s autoionization efficiency which is compatible with unity, within the accuracy of our experiment, for all clusters except those with the lowest Xe content (Xe$_{\rm cl}$ approx. 10-12\,\%).
For the latter, also a decrease of the efficiency with decreasing cluster size is seen. 
Two main reasons can be identified that may cause a decrease in autoionization efficiency. 
Firstly, in small clusters with a low Xe content, for some Ar atoms no Xe partners allowing either ICD or ETMD might be available.
A simple example are clusters containing just a single Xe atom.
This mechanism would gain in importance for cluster ensembles with small $\langle N\rangle$.
Secondly, if only Xe partners at very large distances are available, ICD might be outpaced by other decay processes, most importantly fluorescence.
}}

@@

 \item \emph{The authors mention that the ‘nuclear dynamics may play an important role’ but that they have been neglected in the calculations. While I understand that it is not feasible in such large systems the authors should at least briefly discuss the possible effect of nuclear dynamics e.g. peak shifts, broadening, ICD vs. ETMD, etc. }\vspace{0.3cm}\\
       We added two paragraphs at the end of the theoretical results section
       discussing the possible effects of nuclear dynamics:\\
       {\color{blue}{All these results neglect the effect of nuclear dynamics, which might affect the spectra. Possible reasons are distance dependent channel closings and openings, a different distribution of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be far less severe in clusters than in dimers or trimers. Additionally, the
elongation of one interatomic distance in a cluster automatically results in the shortening of a different interatomic distance, which will reduce the overall effect. Therefore, there will be a broader spectrum of final state charge
distances $d$ resulting in a broadening of the peak. This was taken into
account by folding the stick spectrum with Gaussians with a width of 300 meV and 600 meV for the ICD and ETMD(3), respectively. While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved. It was therefore guessed to be twice the width of the ICD peak.

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence a decrease of the decay width. 
Since the peaks in the convoluted spectrum 
contain contributions from several atom pairs at different distances, 
this would result
in a small peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
clusters see Ref. 58.
}}

@@

 \item \emph{The spin-orbit splitting of the Ar 3p$^{-1}$ state is briefly mentioned in Table 3 in the experimental section but it also stated that the a single value of the binding energy of Ar 3p equal to 15.3 eV is used for all of the simulations. The authors should explain the motivation for this choice in the theory section.}

The reason is that the clusters do not show spin-orbit splitting as opposed to the monomer. To make this more clear we have included a sentence in the "outer valence" section: {\color{blue}{ A distinction between the Ar 3p $_{1/2}$ and the Ar 3p $_{3/2}$ derived cluster bands can therefore not be made.}}

 \item \emph{Page 13:
       The authors should justify the use of the ‘unified force field’ method for the calculation f the cluster structure (p13).}
       We added a sentence to justify our choice:\\
       After that, the cluster structures were optimized using the unified
       force field implemented in the Avogadro programme
       (version 1.1.0)$^{51,52}$ to give local minimum structures.
       {\color{blue}{ The method
       was chosen due to its low computational cost, the possibility to find
       the next local minimum structure based on the chosen starting point
       and the necessary effort to produce reliable results with density
       functional theory (DFT) for v. d. Waals interactions since in
       this work we discuss structural trends and not absolute structures.}}

### 2016-08-15 theo_results.tex
correct one sentence

All these results neglect the effect of nuclear dynamics, which might
affect the spectra. Possible reasons are distance dependent channel closings
and openings,
a different distribution of interatomic distances due to vibrations
and their different impact on
the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
nuclear dynamics increases the decay width by approximately a factor 2
\cite{Schnorr15}.
However, the atomic displacement can be expected to be far less severe
in clusters than in dimers or trimers. Additionally, 
the elongation of one interatomic distance in a cluster
automatically results in
the shortening of a different interatomic distance, which will reduce
the overall effect. Therefore, there will be a broader spectrum charges in the
final state $d$ resulting in a broadening of the peak. This was taken into
account by folding the stick spectrum with Gaussians with a width of
\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
While the width of the ICD peaks was estimated from the potential energy
surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
with three degrees of freedom involved. It was therefore guessed to be twice the
width of the ICD peak.

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters, treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence decrease the decay width. Since the folded peaks
are constituted from several pairs of different distances, it would result
in a slight peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
in clusters see Ref. \citenum{fasshauernjp}

>>>>

All these results neglect the effect of nuclear dynamics, which might
affect the spectra. Possible reasons are distance dependent channel closings
and openings,
a different distribution of interatomic distances due to vibrations
and their different impact on
the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of
nuclear dynamics increases the decay width by approximately a factor 2
\cite{Schnorr15}.
However, the atomic displacement can be expected to be far less severe
in clusters than in dimers or trimers. Additionally, 
the elongation of one interatomic distance in a cluster
automatically results in
the shortening of a different interatomic distance, which will reduce
the overall effect. Therefore, there will be a broader spectrum  of final
state charge distances
$d$ resulting in a broadening of the peak. This was taken into
account by folding the stick spectrum with Gaussians with a width of
\unit[300]{meV} and \unit[600]{meV} for the ICD and ETMD(3), respectively.
While the width of the ICD peaks was estimated from the potential energy
surface of the ArXe dimer, the situation is more complex in case of the ETMD(3)
with three degrees of freedom involved. It was therefore guessed to be twice the
width of the ICD peak.

The channel closing due to shortening of the interatomic distance is not
relevant for the ETMD(3) process in the ArXe clusters treated in this work,
because this would require unnaturally short interatomic distances.
However, for the ICD it might result in a lower number of pairs with open
decay channels and hence a decrease of the decay width. 
Since the peaks in the convoluted spectrum 
contain contributions from several atom pairs at different distances, 
this would result
in a small peak shift to higher energies of the combined peak at lowest energy.
For a more detailed discussion of nuclear dynamics for the ICD in dimers vs.
clusters see Ref. \citenum{fasshauernjp}
